%------------------------
% ATS-Optimized Resume Template
%------------------------

\documentclass[a4paper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex, hidelinks]{hyperref}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}

\urlstyle{rm}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% ATS-friendly section formatting: no \scshape, no decorative elements
\titleformat{\section}{
  \vspace{-8pt}\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-6pt}]

% Simple resume item without nested bold+colon formatting
\newcommand{\resumeItem}[2]{
  \item\small{\textbf{#1}: #2}
}

% Subheading: bold name, plain date/location
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0.15in]}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-2pt}}

\begin{document}

%----------HEADING-----------------
\begin{center}
  {\LARGE \textbf{Ashmit Saxena}}\\[4pt]
  saxenaashmit85@gmail.com \textbar{} +91-8873294522\\[2pt]
  \href{https://www.linkedin.com/in/ashmit-saxena08}{linkedin.com/in/ashmit-saxena08} \textbar{}
  \href{https://github.com/ashmittt08}{github.com/ashmittt08}
\end{center}

%-----------EDUCATION-----------------
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Vellore Institute of Technology, Bhopal}{Madhya Pradesh, India}
    {B.Tech, Computer Science (Gaming Technology); CGPA: 8.0/10.0}{November 2023 -- May 2027}
\resumeSubHeadingListEnd

%-----------EXPERIENCE-----------------
\section{Experience}
\resumeSubHeadingListStart
  \resumeSubheading
    {CodSoft}{Remote}
    {C++ Programming Intern}{Sep 2024 -- Oct 2024}
  \resumeItemListStart
    \item Developed a console-based application (Number Guessing Game) using input validation and control flow logic.
    \item Built a Student Management System using Object-Oriented Programming (OOP) to manage structured data with CRUD operations.
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart

  \resumeSubheading
    {MentorBoard -- Internship Collaboration Dashboard}{React, TypeScript, Zustand, Tailwind CSS}
    {\href{https://github.com/ashmittt08/MentorBoard}{github.com/ashmittt08/MentorBoard}}{}
  \resumeItemListStart
    \item Designed and developed a React-based web application to manage tasks, standups, and feedback workflows in a collaborative environment.
    \item Implemented a drag-and-drop Kanban board using dnd-kit with efficient state management via Zustand.
    \item Built interactive analytics dashboards using Recharts to visualize task completion and user activity trends.
    \item Implemented data handling and storage using localStorage, applying database management concepts for structured data.
    \item Applied problem-solving and debugging techniques to ensure smooth UI interactions and reliable state updates.
  \resumeItemListEnd

  \resumeSubheading
    {EcoVerse AR -- Augmented Reality Educational Application}{Unity, CSharp, Vuforia}
    {\href{https://github.com/ashmittt08/EcoVerse_ar}{\nolinkurl{github.com/ashmittt08/EcoVerse_ar}}}{}
  \resumeItemListStart
    \item Developed an AR educational mobile application using Unity and Vuforia, rendering interactive 3D models on image targets.
    \item Designed UI/UX flow and optimized assets to ensure smooth performance on Android devices.
  \resumeItemListEnd

\resumeSubHeadingListEnd

%-----------SKILLS-----------------
\section{Skills}
\resumeSubHeadingListStart
  \resumeItem{Programming Languages}{C++, Python, CSharp, JavaScript, HTML, CSS, TypeScript}
  \resumeItem{Frameworks and Libraries}{React, Zustand, Tailwind CSS, Recharts, dnd-kit}
  \resumeItem{Tools and Platforms}{Unity, Git, GitHub, VS Code, Postman, Blender, REST APIs}
  \resumeItem{Core Computer Science Concepts}{Data Structures and Algorithms, Object-Oriented Programming (OOP), Database Management Systems (DBMS), SQL, Problem Solving, Debugging, AR/VR Development, Game Development}
\resumeSubHeadingListEnd

%-----------POSITIONS OF RESPONSIBILITY-----------------
\section{Positions of Responsibility}
\resumeSubHeadingListStart
  \resumeSubheading
    {Virtual Reality and Gaming Club (VRGC), VIT Bhopal}{VIT Bhopal}
    {Social Media Team Member}{}
  \resumeItemListStart
    \item Managed and scheduled content across social media platforms, improving reach and engagement.
    \item Coordinated promotional campaigns for technical events and workshops, increasing participation and visibility.
  \resumeItemListEnd
\resumeSubHeadingListEnd

%-----------ACHIEVEMENTS AND CERTIFICATIONS-----------------
\section{Achievements and Certifications}
\begin{itemize}[leftmargin=0.15in, label={--}]
  \item \small{\textbf{Competitive Programming:} Solved 300+ DSA problems across LeetCode, CodeChef, Codeforces, and GeeksforGeeks.}
  \item \small{\textbf{Codeforces:} Achieved a peak rating of 568.}
  \item \small{\textbf{Postman API Fundamentals Student Expert} -- Certified in API testing and development workflows.}
  \item \small{\textbf{NPTEL Elite Certificate} -- Human Computer Interaction (HCI).}
  \item \small{\textbf{Music:} Senior Diploma in Instrumental (Guitar), Prayag Sangeet Samiti.}
\end{itemize}

\end{document}
